### 2014-03-01 paper/concrete.tex

\begin{definition}[Isomorphism of information-flow control languages]
  A language |(C, .->, erasef l)| is \textit{isomorphic} to a
  language |(C', tarrow', erasefp l)| if there exist total functions |f
  : C -> C'| and |finv : C' -> C'| such that |f .. finv = idf C| |finv
  .. f = idf C'|.  Furthermore, |f| and |finv| are functorial (e.g. if
  $x'\ R'\ y'$ then $f(x')\ R\ f(y')$) over both
  $l$-equivalences and |.->|.

@@

\begin{theorem}[Isomorphism preserves termination sensitive non-interference]
  \label{thm:iso-tsni}
  If \ifc{L} is isomorphic to \tar{L} and \ifc{L} satisfies TSNI, then
  \tar{L} satisfies TSNI.
\end{theorem}

\begin{proof}
  Shown by transporting configurations and reduction derivations from
  \tar{L} to \ifc{L}, applying TSNI, and then transporting the
  resulting configuration, $l$-equivalence and multi-step derivation back.
\end{proof}

\begin{theorem}[Weak isomorphism preserves termination insensitive non-interference]
  \label{thm:iso-tini}
  If a language \con{L} is weakly isomorphic to a language \abs{L}, and \abs{L}
  satisfies TINI, then \con{L} satisfies TINI.
\end{theorem}

\begin{proof}
  Shown by transporting configurations and reduction derivations
  from \con{L} to \abs{L}, applying TINI and transporting the resulting
  equivalence back using functoriality of |finv| over $l$-equivalences.
\end{proof}

>>>>

\begin{definition}[Isomorphism of information-flow control languages]
  A language |(C, .->, erasef l)| is \textit{isomorphic} to a
  language |(C', tarrow', erasefp l)| if there exist total functions |f
  : C -> C'| and |finv : C' -> C| such that |f .. finv = idf C| |finv
  .. f = idf C'|.  Furthermore, |f| and |finv| are functorial (e.g. if
  $x'\ R'\ y'$ then $f(x')\ R\ f(y')$) over both
  $l$-equivalences and |.->|.

@@

\begin{theorem}[Isomorphism preserves termination sensitive non-interference]
  \label{thm:iso-tsni}
  If L is isomorphic to L' and L' satisfies TSNI, then
  L satisfies TSNI.
\end{theorem}

\begin{proof}
  Shown by transporting configurations and reduction derivations from
  L to L', applying TSNI, and then transporting the
  resulting configuration, $l$-equivalence and multi-step derivation back.
\end{proof}

\begin{theorem}[Weak isomorphism preserves termination insensitive non-interference]
  \label{thm:iso-tini}
  If a language L is weakly isomorphic to a language L', and L'
  satisfies TINI, then L satisfies TINI.
\end{theorem}

\begin{proof}
  Shown by transporting configurations and reduction derivations
  from L to L', applying TINI and transporting the resulting
  equivalence back using functoriality of |finv| over $l$-equivalences.
\end{proof}

### 2014-03-01 paper/real.tex

JavaScript (JS), as specified by ECMAScript~\tocite{}, does not have any
built-in functionality for I/O.
%
Consequently, and in contrast to our C and Haskell embeddings, for
which we must eliminate external effects, the embedding for JS is
trivial.
%
Hence, as a first step, we implement the IFC language functionality in the
JS runtime and expose the new functions, e.g., |fork|, by attaching
them to the JS global object.
%
Importantly, each task runs a separate instances of this runtime.

>>>>

JavaScript (JS), as specified by ECMAScript~\tocite{}, does not have any
built-in functionality for I/O.
%
Consequently, and in contrast to our C and Haskell embeddings---for
which we must eliminate external effects---the embedding for JS is
trivial.
%
As a first step, we directly implement |specLangJS roundrobinf| by
running multiple instances of the JS runtime, i.e., |targetLangJS|, in
separate OS-level threads.

Specifically, we implement the IFC language functionality in the JS
runtime, much like browser layout engines implement the DOM, and
expose the new functions, e.g., |fork|, by attaching them to the JS
global object.
%
Importantly, each task created with |fork| is execute in a separate
thread, running a separate, fresh instance of our modified JS runtime.
%
In the context of our formalism, this amounts to using |klone(tS) =
tS0|, where |tS0| is the global object corresponding to the standard
JS library (e.g., |tS0| contains \texttt{Object}, \texttt{Array},
etc.).

Since this implementation approach relies on multiple runtimes of the
language, sending arbitrary objects between tasks can result in
unexpected behavior, e.g., when the object contains reference.
%
Hence, as discussed in Section~\ref{sec:concrete} we restrict |send|
to expressions that can be marshalled as strings, i.e., structurally
clonable objects~\tocite{}.
%
In our formalization this amounts to restricting the IFC language rule
for |send| as follows:
  \Red{HERE: typeof!!!}
